Argennon: A Scalable Cloud Based Smart Contract Platform

### 2022-08-13 tex/sections/incentive.tex
Update abstract, fix typos and add draw.io diagram (#12)
* changed chapter 1 of whitepaper

* changed chapter 1 of whitepaper some more

* create folder for diagrams

* Added Argennon-fees.drawio

* remove empty file

* Update Argennon-fees.drawio

* typos, change PV-DB to PVC, and change confusing sentence

Co-authored-by: Behrouz <behrouz_ayati@yahoo.com>

Only behaviours will be punished that can not happen due to a mistake or an attack. These behaviours include:
\begin{itemize}
    \item Signing a certificate for a block that is not conditionally valid.
    \item Signing a certificate for two different blocks at the same height if none of them
    is a fork block or a seal block.\footnote{Signing
    a fork block and a normal block at the same height usually is a malicious behaviour. However, it will not be
    penalized because there are circumstances that an honest user could mistakenly do that.}
\end{itemize}

\subsection{Incentives for PV-DB Servers}\label{subsec:PV-DB-servers}

The incentive mechanism for PV-DB servers should have the following properties:

\begin{itemize}
    \item It incentivizes storing all storage pages and not only those pages that are used more frequently.
    \item It incentivizes PV-DB servers to actively provide the required storage pages for validators.
    \item Making more accounts will not provide any advantage for a PV-DB server.
\end{itemize}

For our incentive mechanism, we require that every time a validator receives a storage page from a PV-DB, after
validating the data, he gives a receipt to the PV-DB server. In this receipt the validator signs the
following information:

\begin{itemize}
    \item \texttt{ownerAddr}: the account address of the PV-DB server.
    \item \texttt{receivedPageID}: the ID of the received page.
    \item \texttt{round}: the current block number.
\end{itemize}

\note{In a round, an honest validator never gives a receipt for an identical page to two different PV-DB servers.}

To incentivize PV-DB servers, a lottery will be held every round,\footnote{A round is the time interval between
two consecutive blocks.} and a predefined amount of ARGs from
\texttt{dbFeeSink} account will be distributed between the winners as a prize. This prize will be divided equally
between all \emph{winning tickets} of the lottery.

\note{One PV-DB server could own multiple winning tickets in a round.}

@@

\begin{itemize}
    \item The signer was a member of the validators' committee of the block $r - 1$ and signed the block certificate.
    \item The page in the receipt was needed for validating the \textbf{previous} block.
    \item The receipt round number is $r - 1$.
    \item The signer did not sign a receipt for the same storage page for two different PV-DB servers in
    the previous round.
\end{itemize}
For selecting the winning receipts we could use a random generator:
\begin{verbatim}
IF random(seed|validatorPK|receivedPageID) < winProbability THEN
    the receipt issued by validatorPK for receivedPageID is a winner
\end{verbatim}
\begin{itemize}
    \item \texttt{random()} produces uniform random numbers between 0 and 1, using its input argument as a seed.
    \item \texttt{validatorPK} is the public key of the signer of the receipt.
    \item \texttt{receivedPageID} is the ID of the storage page that the receipt was issued for.
    \item \texttt{winProbability} is the probability of winning in every round.
    \item \texttt{seed} is the current block seed.
    \item \texttt{|} is the concatenation operator.
\end{itemize}

Also, based on the current block seed, a random storage page is
selected as the challenge of the round. A PV-DB server that owns a winning receipt needs to broadcast a \emph{winning
ticket} to claim his prize. The winning ticket consists of a winning receipt and a \emph{solution} to the round
challenge. Solving a round challenge requires the content of the storage page which was selected as the round
challenge. This will encourage PV-DB servers to store all storage pages.

>>>>

Punishable behaviours include:
\begin{itemize}
    \item Signing a certificate for a block that is not conditionally valid.
    \item Signing a certificate for two different blocks at the same height if none of them
    is a fork block or a seal block.\footnote{Signing
    a fork block and a normal block at the same height usually is a malicious behaviour. However, it will not be
    penalized because there are circumstances that an honest user could mistakenly do that.}
\end{itemize}

\subsection{Incentives for PVC Servers}\label{subsec:PVC-servers}

The incentive mechanism for PVC servers should have the following properties:

\begin{itemize}
    \item It incentivizes storing all storage pages and not only those pages that are used more frequently.
    \item It incentivizes PVC servers to actively provide the required storage pages for validators.
    \item Making more accounts will not provide any advantage for a PVC server.
\end{itemize}

For our incentive mechanism, we require that every time a validator receives a storage page from a PVC, after
validating the data, he gives a receipt to the PVC server. In this receipt the validator signs the
following information:

\begin{itemize}
    \item \texttt{ownerAddr}: the account address of the PVC server.
    \item \texttt{receivedPageID}: the ID of the received page.
    \item \texttt{round}: the current block number.
\end{itemize}

\note{In a round, an honest validator never gives a receipt for an identical page to two different PVC servers.}

To incentivize PVC servers, a lottery will be held every round,\footnote{A round is the time interval between
two consecutive blocks.} and a predefined amount of ARGs from
\texttt{dbFeeSink} account will be distributed between the winners as a prize. This prize will be divided equally
between all \emph{winning tickets} of the lottery.

\note{One PVC server could own multiple winning tickets in a round.}

@@

\begin{itemize}
    \item The signer was a member of the validators' committee of the block $r - 1$ and signed the block certificate.
    \item The page in the receipt was needed for validating the \textbf{previous} block.
    \item The receipt round number is $r - 1$.
    \item The signer did not sign a receipt for the same storage page for two different PVC servers in
    the previous round.
\end{itemize}
For selecting the winning receipts we could use a random generator:
\begin{verbatim}
IF random(seed|validatorPK|receivedPageID) < winProbability THEN
    the receipt issued by validatorPK for receivedPageID is a winner
\end{verbatim}
\begin{itemize}
    \item \texttt{random()} produces uniform random numbers between 0 and 1, using its input argument as a seed.
    \item \texttt{validatorPK} is the public key of the signer of the receipt.
    \item \texttt{receivedPageID} is the ID of the storage page that the receipt was issued for.
    \item \texttt{winProbability} is the probability of winning in every round.
    \item \texttt{seed} is the current block seed.
    \item \texttt{|} is the concatenation operator.
\end{itemize}

Also, based on the current block seed, a random storage page is
selected as the challenge of the round. A PVC server that owns a winning receipt needs to broadcast a \emph{winning
ticket} to claim his prize. The winning ticket consists of a winning receipt and a \emph{solution} to the round
challenge. Solving a round challenge requires the content of the storage page which was selected as the round
challenge. This will encourage PVC servers to store all storage pages.
